Evaluating preciseTAD parameters

### 2020-08-14 Scripts_for_results/14_evaluating_preciseTAD_parameters.Rmd
updated figures and tables

df <- data.frame(Overlap = c(length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt_95_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_1_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_1_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_1_10000_22[[2]])-.1,

length(unique(subjectHits(findOverlaps(flank(pt_99_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_99_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_99_10000_22[[2]]),

length(unique(subjectHits(findOverlaps(flank(pt_975_1000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_1000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_975_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_975_10000_22[[2]]),

NA,
length(unique(subjectHits(findOverlaps(flank(pt_95_2500_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_2500_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_5000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_5000_22[[2]]),
length(unique(subjectHits(findOverlaps(flank(pt_95_10000_22[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt_95_10000_22[[2]])),

Threshold = c(rep(c(rep("t=1.0",4),
              rep("t=0.99",4),
              rep("t=0.975",4),
              rep("t=0.95",4)),4)),

Epsilon = rep(c("eps=1000",
              "eps=2500",
			  "eps=5000",
			  "eps=10000"),16),

Annotation = c(rep("CTCF", 16),
               rep("RAD21", 16),
			   rep("SMC3", 16),
			   rep("ZNF143", 16))
)

df$Epsilon <- factor(df$Epsilon, levels=c("eps=1000", "eps=2500", "eps=5000", "eps=10000"))

ggplot(data=df, aes(x=Annotation, y=Overlap, fill=Annotation)) +
  facet_grid(Epsilon ~ Threshold) +
  geom_bar(stat='identity') +
  ylim(0,1.5)+
  ylab("Normalized Overlap") +
  xlab("Annotation") +
  guides(fill=FALSE) +
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size=10,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.background.x = element_blank(),
        #strip.background.y = element_blank(),
        legend.text=element_text(size=10),
        legend.title=element_text(size=15),
        plot.title = element_text(size=15))
```

>>>>

t = c(".95",".975",".99","1.0")
eps = c(5000,10000,15000,20000,25000)

NO1_ctcf = numeric()
NO2_ctcf = numeric()
NO3_ctcf = numeric()
for(i in 1:length(t)){
  for(j in 1:length(eps)){
    print(c(t[i], eps[j]))

    if(t[i]=="1.0" & eps[j]==5000){
      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
    }else{
      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
                           t[i],
                           ".",
                           eps[j],
                           ".rds"))
    }

    NO1_ctcf = rbind(NO1_ctcf,
                length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt[[2]]))

    NO2_ctcf = rbind(NO2_ctcf,
                length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))/length(pt[[2]]))

    NO3_ctcf = rbind(NO3_ctcf,
                length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[1]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[1]]))$distance)+1))/length(pt[[2]]))

  }
}

NO1_rad21 = numeric()
NO2_rad21 = numeric()
NO3_rad21 = numeric()
for(i in 1:length(t)){
  for(j in 1:length(eps)){
    print(c(t[i], eps[j]))

    if(t[i]=="1.0" & eps[j]==5000){
      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
    }else{
      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
                           t[i],
                           ".",
                           eps[j],
                           ".rds"))
    }

    NO1_rad21 = rbind(NO1_rad21,
                     length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt[[2]]))

    NO2_rad21 = rbind(NO2_rad21,
                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))/length(pt[[2]]))

    NO3_rad21 = rbind(NO3_rad21,
                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[2]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[2]]))$distance)+1))/length(pt[[2]]))

  }
}

NO1_smc3 = numeric()
NO2_smc3 = numeric()
NO3_smc3 = numeric()
for(i in 1:length(t)){
  for(j in 1:length(eps)){
    print(c(t[i], eps[j]))

    if(t[i]=="1.0" & eps[j]==5000){
      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
    }else{
      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
                           t[i],
                           ".",
                           eps[j],
                           ".rds"))
    }

    NO1_smc3 = rbind(NO1_smc3,
                      length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt[[2]]))

    NO2_smc3 = rbind(NO2_smc3,
                      length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))/length(pt[[2]]))

    NO3_smc3 = rbind(NO3_smc3,
                      length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[3]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[3]]))$distance)+1))/length(pt[[2]]))

  }
}

NO1_znf143 = numeric()
NO2_znf143 = numeric()
NO3_znf143 = numeric()
for(i in 1:length(t)){
  for(j in 1:length(eps)){
    print(c(t[i], eps[j]))

    if(t[i]=="1.0" & eps[j]==5000){
      pt <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
    }else{
      pt <- readRDS(paste0("Z:/TAD_data_analysis/miscellaneous/evaluating_preciseTAD_parameters/chr22/pt",
                           t[i],
                           ".",
                           eps[j],
                           ".rds"))
    }

    NO1_znf143 = rbind(NO1_znf143,
                     length(unique(subjectHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt[[2]]))

    NO2_znf143 = rbind(NO2_znf143,
                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))/length(pt[[2]]))

    NO3_znf143 = rbind(NO3_znf143,
                     length(unique(queryHits(findOverlaps(flank(pt[[2]], width = 5000, both = TRUE),genomicElements.GR[[4]]))))*(1/(mean(mcols(distanceToNearest(pt[[2]],genomicElements.GR[[4]]))$distance)+1))/length(pt[[2]]))

  }
}

params_df <- rbind.data.frame(cbind(NO1_ctcf,NO2_ctcf,NO3_ctcf),
      cbind(NO1_rad21,NO2_rad21,NO3_rad21),
      cbind(NO1_smc3,NO2_smc3,NO3_smc3),
      cbind(NO1_znf143,NO2_znf143,NO3_znf143))
params_df$Threshold <- rep(c(rep("0.95", 5),
                         rep("0.975", 5),
                         rep("0.99", 5),
                         rep("1.0", 5)),4)
params_df$eps <- rep(c("5000","10000","15000","20000","25000"), 4*4)
params_df$eps <- factor(params_df$eps, levels=c("5000","10000","15000","20000","25000"))
params_df$Annotation <- c(rep("CTCF", 20),
                          rep("RAD21", 20),
                          rep("SMC3", 20),
                          rep("ZNF143", 20))

ggplot(params_df, aes(x=eps, y=V1, color=Annotation, group=Annotation)) +
  facet_grid(. ~ Threshold)+
  geom_line(size=2, position=position_dodge(0.5))+
  geom_point(size=5, position=position_dodge(0.5))+
  theme_minimal() +
  theme_bw()+
  xlab("eps") + 
  ylab("Normalized Overlap") + 
  theme(axis.text.x = element_text(size=15,
                                   angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
  ),
  axis.text.y = element_text(size = 15),
  axis.title.x = element_text(size = 20),
  axis.title.y = element_text(size = 20),
  strip.text.x = element_text(size = 15),
  strip.text.y = element_text(size = 15),
  legend.text=element_text(size=15),
  legend.title=element_text(size=20),
  plot.title = element_text(size=20),
  legend.position="bottom")
```
